SVG: The Paper

### 2022-07-04 Analysis/index.Rmd
timing trial model

```{r, message=FALSE}
# attach packages
library(tidyverse)
library(patchwork)
library(tidybayes)
library(ggrepel)
library(truncnorm)
```

@@

## Are more predictable people faster at the task?

```{r}
drt <- filter(d, found == 40) %>% group_by(observer, condition) %>%
  summarise(median_rt = median(RT), .groups = "drop") %>% 
  full_join(dm, by = c("observer", "condition"))

ggplot(drt, aes(accuracy, median_rt, colour = condition)) +
         geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm")

summary(lm(median_rt ~ accuracy*condition, data = drt))

drt <- filter(d, found == 40)

@@

```{r}
# try doing per trial
a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  group_by(observer, condition, trial) %>%
  summarise(time_taken = max(RT),
            acc = mean(selected_max, na.rm = T), 
            .groups = "drop") %>%
  filter(time_taken < 60)  ->timedat

timedat %>%
  ggplot(aes(time_taken, acc, colour = condition)) + 
  geom_jitter(alpha = 0.2, height = 0.005, width = 0) +
  geom_smooth(method = "lm") + 
  facet_wrap(~condition)

# library(brms)
# 
# my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)

>>>>

```{r, message=FALSE}
# attach packages
library(tidyverse)
library(patchwork)
library(tidybayes)
library(ggrepel)
library(truncnorm)
library(modelr)
library(brms)
```

@@

## The relationship between time and model accuracy

### Faster people are more predictable

Is this worth doing?

### Shorter trials are more predictable

```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is. Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model. The lines give posterior samples from each indivdiaul observer."}
a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  group_by(observer, condition, trial) %>%
  summarise(time_taken = max(RT),
            acc = mean(selected_max, na.rm = T), 
            .groups = "drop") %>%
  filter(time_taken < 60) %>%
  mutate(time_taken_s = as.numeric(scale(log(time_taken)))) -> timedat

write_csv(timedat, "scratch/time_per_trial.csv")

m <- readRDS("scratch/time_model_acc_model.rds")

fixef(m) %>% knitr::kable()

@@

```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is. Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model. The lines give posterior samples from each indivdiaul observer."}
timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
  add_epred_draws(m, re_formula = NA, ndraws = 100) %>%
  ggplot(aes(time_taken_s, fill = condition)) + 
  stat_lineribbon(aes(y = .epred), alpha = 0.5, .width = c(0.53, 0.97)) +
  geom_jitter(data = timedat, aes(y = acc, colour = condition), 
              alpha = 0.05, width = 0, height = 0.005, colour = "black") +
  scale_x_continuous("scaled log response time (log seconds)") + 
  scale_y_continuous("model accuracy")  + 
  scale_colour_discrete(guide = "none") +
  coord_cartesian(ylim = c(0.4, 0.9)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  facet_wrap(~ condition) -> plt

timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5), observer) %>%
  add_epred_draws(m, re_formula = NULL, ndraws = 1) -> d_pred

plt + geom_path(data  = d_pred,
                aes(y = .epred, 
                    group = interaction(condition, observer)),
                alpha = 0.25)

# 
# my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)
